Advice on describing Bayesian analysis of neutron and X-ray reflectometry

### 2022-11-16 src/tex/ms.tex
Update ESI DOI

Electronic Supplementary Information (ESI) available: All analysis/plotting scripts and data files allowing for a fully reproducible and automated analysis workflow, using \showyourwork~\cite{luger_showyourwork_2022,luger_mapping_2011}, for this work is available at \url{https://github.com/arm61/reporting_sampling} (DOI:\ 10.5281/zenodo.6874560) under an MIT license, while the paper is shared under a CC BY-SA 4.0 license~\cite{mccluskey_github_2022} and the data shown in Figure~\ref{fig:post} is also available under a CC BY-SA 4.0 license~\cite{caruana_zenodo_2022}.

>>>>

Electronic Supplementary Information (ESI) available: All analysis/plotting scripts and data files allowing for a fully reproducible and automated analysis workflow, using \showyourwork~\cite{luger_showyourwork_2022,luger_mapping_2011}, for this work is available at \url{https://github.com/arm61/reporting_sampling} (DOI:\ 10.5281/zenodo.7326091) under an MIT license, while the paper is shared under a CC BY-SA 4.0 license~\cite{mccluskey_github_2022} and the data shown in Figure~\ref{fig:post} is also available under a CC BY-SA 4.0 license~\cite{caruana_zenodo_2022}.
